Coexistence with varying environmental filtering intensity

### 2018-08-14 env_intensity.Rmd
Package directlabels loaded.
:sparkles: Compute theoretical growth rate
Co-authored-by: pierredenelle <pierre.denelle@cefe.cnrs.fr>
Co-authored-by: Rekyt <matthias.grenie@ens-lyon.fr>

library("cowplot")
library("tidyverse")
library("FD")

@@

>>>>

library("cowplot")
library("tidyverse")
library("FD")
library("directlabels")

@@

```{r}
sp_growth_all_patch = apply(traits, 1, function(x) {
    lapply(env, function(y) {
        env_curve(x, y, trait_weights = trait_types$RA20, k = k, width = 10)
    })
})

lapply(sp_growth_all_patch, function(given_list) {
    data.frame(ID = rep(names(given_list), sapply(given_list, length)),
               Obs = unlist(given_list))
}) %>%
    bind_rows(.id = "species") -> sp_growth_df

sp_growth_df %>%
    rename(patch = ID,
           growth_rate = Obs) -> sp_growth_df

sp_growth_df %>%
    mutate(patch_optim = as.numeric(gsub("patches", "", patch))) -> sp_growth_df

sp_growth_df %>%
    inner_join(traits %>%
                   as.data.frame() %>%
                   rownames_to_column("species"),
               by = "species") -> sp_growth_df

plot_env_trait1_rate = ggplot(sp_growth_df, aes(patch_optim, trait1, z = growth_rate)) +
    stat_summary_2d(geom = "raster", bins = 17, interpolate = TRUE) +
    scale_fill_viridis_c() +
    labs(x = "Environment", fill = "Growth Rate",
         y = "Trait 1 (80% weight Growth Rate)") +
    theme_bw() +
    theme(legend.position = "top")

plot_env_trait2_rate = ggplot(sp_growth_df, aes(patch_optim, trait2, z = growth_rate)) +
    stat_summary_2d(geom = "raster", bins = 17, interpolate = TRUE) +
    scale_fill_viridis_c() +
    labs(x = "Environment", fill = "Growth Rate",
         y = "Trait 2 (20% weight Growth Rate)") +
    theme_bw() +
    theme(legend.position = "top")

plot_env_trait3_rate = ggplot(sp_growth_df, aes(patch_optim, trait3, z = growth_rate)) +
    stat_summary_2d(geom = "raster", bins = 17, interpolate = TRUE) +
    scale_fill_viridis_c() +
    labs(x = "Environment", fill = "Growth Rate",
         y = "Trait 3 (0% weight Growth Rate)") +
    theme_bw() +
    theme(legend.position = "top")

plot_grid(plot_env_trait1_rate, plot_env_trait2_rate, plot_env_trait3_rate, ncol = 3)
```
